### 2022-04-07 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_betacov_mapping@a2dd8bb55c0522d53f67019ac72781b93953140b 🚀

        {\bfseries Purpose:}\,This template provides a series of scripts
to render a markdown document into an interactive website and a series
of PDFs.\\%
        {\bfseries Motivation:}\,It makes collaborating on text with
GitHub easier, and means that we never need to think about the
output.\\%
        {\bfseries Internals:}\,GitHub actions and a series of python
scritpts. The markdown is handled with \texttt{pandoc}.\\%

>>>>

\vfill
Coming soon

### 2022-04-07 preprint.tex
Deploying to gh-pages from @ PoisotLab/ms_betacov_mapping@a2dd8bb55c0522d53f67019ac72781b93953140b 🚀

        {\bfseries Purpose:}\,This template provides a series of scripts
to render a markdown document into an interactive website and a series
of PDFs.\\%
        {\bfseries Motivation:}\,It makes collaborating on text with
GitHub easier, and means that we never need to think about the
output.\\%
        {\bfseries Internals:}\,GitHub actions and a series of python
scritpts. The markdown is handled with \texttt{pandoc}.\\%

>>>>

Coming soon
